### 2024-08-14 parts/appendix.tex
gigantic rewrite

\begin{proofof}[decompose-polynomial:lem]
    Let us first write $f \in \ZPoly$ as a linear combination 
    $f = f_+ - f_-$ where both $f_+$ and $f_-$ are in $\NPoly$.

    We apply
    \cref{n-poly-combinatorics:lem} to compute the $\omega$ that works for both $f_+$ and $f_-$.
    Using this $\omega$,
    for any choice of
    $r \defined (r_1, \dots, r_n) \in \set{0, \dots, \omega - 1}$,
    there exists a polynomial $P_r \in \Rel[X_1, \dots, X_p]$
    such that $X_1, \dots, X_p \geq \omega$:
    \begin{equation*}
        f\left(
        a_1^{\omega X_1 + r_1} \cdots a_n ^{\omega X_n + r_n}\right) 
        = P_r(X_1, \dots, X_p) \quad .
    \end{equation*}
    To get the full family of polynomials needed requires
    just to only iterate subsets of letters, and fix the other ones
    to be below the threshold $\omega^2$.
\end{proofof}

>>>>

\begin{proofof}[decompose-polynomial:lem]
    Let us first write $f \in \ZPoly$ as a linear combination 
    $f = f_+ - f_-$ where both $f_+$ and $f_-$ are in $\NPoly$.
    We 
    compute $\omega_+$ (resp. $\omega_-$)
    by
    applying
    \cref{n-poly-combinatorics:lem} 
    to $f_+$ (resp. to $f_-$).
    Finally, let $\omega \defined \ppcm(\omega_+, \omega_-)$.

    Using this $\omega$,
    for any choice of
    $r \defined (r_1, \dots, r_n) \in \set{0, \dots, \omega - 1}$,
    there exists an \kl{integer binomial polynomial}
    $P_r \in \Rel[X_1, \dots, X_p]$,
    obtained as
    the difference of the two \kl{natural binomial polynomial} $P_r^+$ and $P_r^-$
    associated to $f_+$ and $f_-$,
    such that $X_1, \dots, X_p \geq 1$:
    \begin{equation*}
        f\left(
        a_1^{\omega X_1 + r_1} \cdots a_n ^{\omega X_n + r_n}\right) 
        = P_r(X_1, \dots, X_p) \quad .
    \end{equation*}
    We conclude by selecting different values of $r$ and
    setting some subsets of variables to be assigned to the constant $0$.
\end{proofof}

### 2024-08-14 parts/correction.tex
gigantic rewrite

\AP There is still a minor detail that remains to be smoothened before proving
our combinatorial \cref{n-poly-combinatorics:lem}, which is that some
polyregular functions can exhibit a limited form of division. For instance, the
function computing the sum of the lengths of the suffixes of a word $w$
actually computes $\card{w} \times (\card{w} - 1) / 2$. This will be at odds
with our restriction to polynomials with coefficients in $\Rel$. However, we
argue that up to a suitable change of basis for the ring of polynomials, all
coefficients will actually be in $\Nat$. This relatively simple trick works by
considering as ``basic polynomials" the \intro{binomial polynomials} of the
form $\binom{X - \ell}{k}$, where $\ell$ and $k$ are natural numbers. This is
why we introduce the notion of \intro{natural binomial polynomial} as
$\Nat$-linear combinations of products of \kl{binomial polynomials}.

@@

    In all cases, we will use a \kl{polynomial function} $q \colon \Nat^p \to
    \Sigma^*$ defined by $q(X_1, \dots, X_p) \defined \alpha_0 \prod_{i = 1}^p
    (u_i^{\omega \times X_i} \alpha_i)$ using some words $\alpha_i$ ($0 \leq i
    \leq p$) and $u_i$ ($1 \leq i \leq p)$ in $\Sigma^*$. That is, we will
    implicitly multiply all variables by $\omega$ in order to make the
    equations more readable. Note that when using an induction hypothesis, we
    will therefore have to check that the polynomial $q$ will have this
    specific form.

@@

Let us highlight that the multiplicative factor $\omega$ is necessary in
\cref{n-poly-combinatorics:lem}. Indeed, the function $f \colon \set{a}^* \to
\Nat$ defined as $0$ when the input is of odd length and $1$ when the input is
of even length is \kl{$\Nat$-polyregular}, but $f(a^X)$ is not a polynomial.

\begin{corollary}
    \label{n-rat-correct:lem}
    Let $P \in \Rel[X_1, \dots, X_p]$ be an \kl{$\Nat$-rational polynomial}.
    Then,
    $P \in \CorrectPoly$.
    \proofref{n-rat-correct:lem}
\end{corollary}
\begin{proof}
    Let $f$ be the \kl{commutative}
    \kl{$\Nat$-polyregular function}
    with domain defined as $\Sigma \defined \set{a_1, \dots, a_p}$
    that \kl{represents} $P$. 
    Using \cref{n-poly-combinatorics:lem},
    there exists a number $\omega \in \Nat_{\geq 1}$
    and polynomial $Q$ with \kl{non-negative}
    \kl{maximal monomials} such that
    for all $X_1, \dots, X_p \geq \omega$:
    \begin{equation*}
        f\left(
            \prod_{i = 1}^p a_i^{\omega X_i}
        \right)
        = Q(X_1, \dots, X_p)
        = P(\omega X_1, \dots, \omega X_p) 
        \quad .
    \end{equation*}
    We conclude that $P(\omega X_1, \dots, \omega X_p) = Q(X_1, \dots, X_p)$
    as polynomials,
    and in particular that
    the \kl{maximal monomials} of 
    $P$ are \kl{non-negative}.

@@

\begin{fact}
    \label{maxi-monomials-submodular:fact}
    Let $P, Q$ be two polynomials.
    Then, $\MaximalMonomials(P+Q) \hoareleq \MaximalMonomials(P)
    \cup \MaximalMonomials(Q)$.
\end{fact}

\begin{fact}
    \label{translation-maximal:fact}
    For all $P \in \Rel[\vec{X}]$, and $K \in \Nat$,
    \begin{equation*}
        \MaximalMonomials(P) = \MaximalMonomials(\translate{K}(P))
        \quad .
    \end{equation*}
\end{fact}

\textbf{TODO: fix this?}
\begin{fact}
    \label{derivation-monomials:fact}
    Let $K > 0$,
    and let $M,T$ be two \kl{monomials}, such that
    $T$ \kl{strictly divides} $M$.
    Then,
    every \kl{monomial} of $\Diff{K}{M}$ \kl{strictly divides} $M$,
    and 
    $T$ \kl{divides} some \kl{maximal monomial}
    of $\Diff{K}{M}$, which has a coefficient
    that is a multiple of $K$.
\end{fact}
\begin{proof}
    Let $M \defined X_1^{k_1} \cdots X_n^{k_n}$,
    where $k_1, \dots, k_n > 0$ and $n > 0$.
    Let us compute
    \begin{align*}
        \Diff{K}{M} &= \prod_{i = 1}^n X_i^{k_i} - \prod_{i = 1}^n (X_i - K)^{k_i} \\
                    &= \sum_{p = 1}^n \frac{K}{X_p - K} \prod_{i = 1}^n (X_i - K)^{k_i} 
    \end{align*}
    Therefore, 
    the \kl{maximal monomials} of $\Diff{K}{M}$
    are precisely
    of the form $K \frac{\prod_{i = 1}^n X_i^{k_i}}{X_p}$ for some $1 \leq p \leq i$,
    which \kl{strictly divides} $M$.
    Let $T$ be a \kl{monomial} that \kl{strictly divides} $M$,
    then, $T = \prod_{i = 1}^n X_i^{t_i}$, 
    for all $1 \leq i \leq n$, $t_i \leq k_i$,
    and there exists $1 \leq p \leq n$ such that $t_j < k_j$.
    In particular, $T$ \kl{divides}
    $K \frac{\prod_{i = 1}^n X_i^{k_i}}{X_p}$.
\end{proof}

\begin{lemma}
    \label{derivation-simplifies:lemma}
    For all $P \in \Rel[\vec{X}]$ that are non-constant,
    for all $K \in \Nat$,
    $\MaximalMonomials(\Diff{K}{P}) \hoarele
    \MaximalMonomials(P)$.
\end{lemma}
\begin{proof}
    Let $P \in \Rel[\vec{X}]$ and
    $K \in \Nat$.
    Leveraging 
    \cref{derivation-monomials:fact,discrete-deriv-linear:fact,maxi-monomials-submodular:fact}:
    \begin{align*}
        \MaximalMonomials\left(\Diff{K}{P}\right)
        &=
        \MaximalMonomials\left(\sum_{M \in \Monomials(P)} \Diff{K}{M}\right) \\
        &\hoareleq
        \bigcup_{M \in \Monomials(P)} 
        \MaximalMonomials(\Diff{K}{M}) \\
        &\hoarele
        \MaximalMonomials(P)
        & \text{ because } \deg(\Diff{K}{P}) < \deg(P)
    \end{align*}
    Which concludes the proof.
\end{proof}

\begin{lemma}
    \label{derivation-stabilises-correct:lem}
    Let $P \in \CorrectPoly$,
    $P_1$ be the sum of \kl{maximal monomials} of $P$,
    and $P_2 \defined P - P_1$ be the sum of
    non-maximal monomials of $P$.
    There exists a computable number $K \in \Nat$,
    such that
    $Q \defined (\Diff{K}{P_1} + \translate{K}(P_2)) \in \CorrectPoly$.
    \proofref{derivation-stabilises-correct:lem}
\end{lemma}

\begin{lemma}
    \label{lem:correct-to-n-rat}
    Let $\vec{X}$ be a tuple of indeterminates,
    and let $P \in \Rel[\vec{X}]$.
    If $P \in \CorrectPoly$, then $P$ is \kl{represented}
    by a \kl{star-free $\Nat$-polyregular function},
    which is computable given $P$.
\end{lemma}
\begin{proof}
    We prove the result by induction on $\MaximalMonomials(P)$. 
    In the proof, we write $\vec{X}$ for the indeterminates appearing in $P$,
    that is, we assume without loss of generality that all indeterminates are used.

@@

    \textbf{Induction:} Assume that $P$ is not a constant polynomial, and let
    us write $P = P_1 + P_2$ where $P_1$ is the sum of the \kl{maximal
    monomials} of $P$. We compute a bound $K$ such that $Q \defined
    (\Diff{K}{P_1} + \translate{K}(P_2)) \in \CorrectPoly$ using
    \cref{derivation-stabilises-correct:lem}. Thanks to
    \cref{derivation-simplifies:lemma}, we also know that $\MaximalMonomials(Q)
    \hoarele \MaximalMonomials(P)$. By induction hypothesis, $Q$ is
    \kl{represented} by a \kl{star-free $\Nat$-polyregular function} which is
    effectively computable.

    Let us now remark that $P_1 \in \Nat[\vec{X}]$, and is therefore
    (effectively) \kl{represented} by a \kl{star-free $\Nat$-polyregular
    function} (\cref{n-poly-n-poly:example}). As a consequence,
    $\translate{K}(P) = P_1 + Q$ is (effectively) \kl{represented} by a
    function $f_\Delta$.

    For all partial valuations $\nu \colon \vec{X} \topartial \set{0, \dots,
    K}$ fixing at least one indeterminate,  we know that
    $\MaximalMonomials(\restr{P}{\nu}) \hoarele \MaximalMonomials{P}$. Because
    $\restr{P}{\nu} \in \CorrectPoly$, one can use the induction hypothesis to
    compute a \kl{star-free $\Nat$-polyregular function} $f_\nu$ that
    \kl{represents} $\restr{P}{\nu}$. This is possible because we assumed 
    that all indeterminates in $\vec{X}$ are used in $P$.

@@

\begin{lemma}
    \label{derivation-translation:lem}
    Let $\vec{X}$ be a tuple of indeterminates,
    and let $P \in \Rel[\vec{X}]$.
    There exists a computable number $K \in \Nat$
    such that the following are equivalent:
    \begin{enumerate}
        \item \label{d-t-correct:item} $P \in \CorrectPoly$,
        \item \label{d-t-transl:item}
            for 
            all partial functions $\nu \colon \vec{X} \topartial \Nat$,
            $\translate{K}(\restr{P}{\nu}) \in \Nat[\vec{X}]$,
        \item \label{d-t-transl-fin:item}
            for all partial functions
            $\nu \colon \vec{X} \topartial \set{0, \dots, K}$,
            $\translate{K}(\restr{P}{\nu}) \in \Nat[\vec{X}]$.
    \end{enumerate}
    \proofref{derivation-translation:lem}
\end{lemma}

@@

\begin{theorem}
    \label{corrected-version:thm}
    Let $\vec{X}$ be a tuple of indeterminates,
    and let $P \in \Rel[\vec{X}]$.
    The following are equivalent:
    \begin{enumerate}
        \item \label{corrected-1:item} $P \in \CorrectPoly$,
        \item \label{corrected-2:item} $P$ is \kl{represented} by a \kl{$\Nat$-rational series},
        \item \label{corrected-3:item} $P$ is \kl{represented} by a \kl{$\Nat$-polyregular function},
        \item \label{corrected-4:item} $P$ is \kl{represented} by a \kl{star-free $\Nat$-polyregular function},
    \end{enumerate}
    Furthermore, the properties are decidable, and conversions effective.
\end{theorem}
\begin{proof}
    The implications 
    \cref{corrected-4:item} $\implies$
    \cref{corrected-3:item} $\implies$
    \cref{corrected-2:item} are obvious.
    \cref{lem:correct-to-n-rat} proves
    \cref{corrected-1:item} $\implies$ \cref{corrected-4:item},
    while \cref{n-rat-correct:lem}
    proves 
    \cref{corrected-2:item} $\implies$ \cref{corrected-1:item}.
    Note that the lemmas provide effective conversion procedures,
    and that
    \cref{derivation-translation:lem}
    also provides a decision
    procedure.
\end{proof}

@@

>>>>

\AP There is still a minor detail that remains to be smoothened before proving
our combinatorial \cref{n-poly-combinatorics:lem}, which is that some
polyregular functions can exhibit a limited form of division. For instance, the
function computing the sum of the lengths of the suffixes of a word $w$
actually computes $\card{w} \times (\card{w} - 1) / 2$. This will be at odds
with our restriction to polynomials with coefficients in $\Rel$. However, we
argue that up to a suitable change of basis for the ring of polynomials, all
coefficients will actually be in $\Nat$. This relatively simple trick works by
considering as ``basic polynomials" the \intro{binomial monomial} of the form
$\binom{X - \ell}{k}$, where $\ell$ and $k$ are natural numbers. Beware that
$\binom{X - \ell}{k}$ is defined to be $0$ when $X \leq \ell$, and is therefore
a ``true polynomial" only when $X \geq \ell$. This is why we introduce the
notion of \intro{natural binomial polynomials} as $\Nat$-linear combinations of
products of \kl{binomial monomials}.

@@

    In all cases, we will use a \kl{polynomial function} $q \colon \Nat^p \to
    \Sigma^*$ defined by $q(X_1, \dots, X_p) \defined \alpha_0 \prod_{i = 1}^p
    (u_i^{\omega \times X_i} \alpha_i)$ using some words $\alpha_i$ (for $0 \leq i
    \leq p$) and $u_i$ (for $1 \leq i \leq p)$ in $\Sigma^*$. That is, we will
    implicitly multiply all variables by $\omega$ in order to make the
    equations more readable. Note that when using an induction hypothesis, we
    will therefore have to check that the polynomial $q$ will have this
    specific form.

@@

Let us highlight that the multiplicative factor $\omega$ is necessary in
\cref{n-poly-combinatorics:lem}. Indeed, the function $f \colon \set{a}^* \to
\Nat$ defined as $0$ when the input is of odd length and $1$ when the input is
of even length is \kl{$\Nat$-polyregular}, but $f(a^X)$ is not a polynomial.
Let us remark that the \kl{maximal monomials} of the polynomial $\binom{X -
p}{k}$ have coefficient $1/k!$, and are therefore \kl{non-negative}.

\begin{corollary}
    \label{n-rat-correct:lem}
    Let $P \in \Rel[X_1, \dots, X_p]$ be an \kl{$\Nat$-rational polynomial}.
    Then,
    $P \in \CorrectPoly$.
    \proofref{n-rat-correct:lem}
\end{corollary}
\begin{proof}
    Let $f$ be the \kl{commutative}
    \kl{$\Nat$-polyregular function}
    with domain defined as $\Sigma \defined \set{a_1, \dots, a_p}$
    that \kl{represents} $P$. 
    Using \cref{n-poly-combinatorics:lem},
    there exists a number $\omega \in \Nat_{\geq 1}$
    and \kl{natural binomial polynomial} $Q$
    such that
    for all $n_1, \dots, n_p \geq 1$:
    \begin{equation*}
        f\left(
            \prod_{i = 1}^p a_i^{\omega n_i}
        \right)
        = Q(n_1, \dots, n_p)
        = P(\omega n_1, \dots, \omega n_p) 
        \quad .
    \end{equation*}
    We conclude that $P(\omega X_1, \dots, \omega X_p) = Q(X_1, \dots, X_p)$
    as polynomials,
    and in particular that
    the \kl{maximal monomials} of 
    $P$ are \kl{non-negative}.

@@

\begin{lemma}
    \label{all-positive-derivative:lem}
    Let $P \in \Nat[\vec{X}]$ that is non-constant, and $K \in \Nat$,
    then $\Diff{K}{P} \in \Nat[\vec{X}]$ and all of its
    coefficients are (positive) multiples of $K$.
    Furthermore, every monomial that strictly divides some monomial of $P$
    appears in $\Diff{K}{P}$.
\end{lemma}
\begin{proof}
    We prove the result for monomials, as it extends
    to $\Nat$-linear combinations by linearity.
    Let $P = \prod_{i = 1}^k X_i^{\alpha_i}$ be a monomial.
    Notice that $\translate{K}(P) = \prod_{i = 1}^n (X_i + K)^{\alpha_i}$,
    and using a binomial expansion
    we list all the possible divisors of $P$,
    all of which with coefficients that are positive integers and multiples of $K$ except the coefficient
    of the maximal monomial (equal to $P$ itself) which is $1$.
    As a consequence, $\translate{K}(P) - P$ is simply
    obtained by removing this maximal monomial, which concludes the proof.
\end{proof}

\begin{lemma}
    \label{derivation-stabilises-correct:lem}
    Let $P \in \CorrectPoly$,
    $P_1$ be the sum of \kl{maximal monomials} of $P$,
    and $P_2 \defined P - P_1$ be the sum of
    non-maximal monomials of $P$.
    There exists a computable number $K \in \Nat$,
    such that
    $Q \defined (\Diff{K}{P_1} + \translate{K}(P_2)) \in \Nat[\vec{X}]$.
\end{lemma}
\begin{proof}
    Let us first tackle the specific case where $P$ is a constant polynomial.
    In this case, $P_1 = P$ and $P_2 = 0$.
    Furthermore,
    $\translate{K}(P_1) = P_1$ and $\Diff{K}{P_1} = 0$ for all $K \in \Nat$.
    We conclude that $\Diff{K}{P_1} + \translate{K}(P_2) = 0$
    for all $K \in \Nat$, hence belongs to $\Nat[\vec{X}]$. Selecting $K = 0$
    we conclude.

    Assume now that $P$ is not a constant polynomial. We will use
    \cref{all-positive-derivative:lem} on a well-selected value of $K$. Let us
    write $\alpha$ to be the maximal absolute value of a coefficient in $P$.
    Let $D$ be the number of unitary monomials that divide some monomial
    appearing in $P$. We can now define $K \defined D \times \alpha$,
    and let
    $Q \defined (\Diff{K}{P_1} + \translate{K}(P_2))$.
    Remark that $\Diff{K}{P_1}$ is already in $\Nat[\vec{X}]$,
    and the constant term of $\translate{K}(P_2)$ is also
    in $\Nat$.
    For any other monomial of $P_2$, by the maximality of $P_1$,
    it strictly divides some monomial of $P_1$,
    equals some monomial of $\Diff{K}{P_1}$. Because every monomial
    of $\Diff{K}{P_1}$ has a coefficient that is a multiple of $K = \alpha \times D$, we can
    match every monomial of $P_2$ to $\alpha$ copies of a unitary
    monomial appearing in $\Diff{K}{P_1}$, and because $\alpha$ is large enough
    we conclude that 
    $Q \in \Nat[\vec{X}]$.
\end{proof}

\begin{lemma}
    \label{lem:correct-to-n-rat}
    Let $\vec{X}$ be a tuple of indeterminates,
    and let $P \in \Rel[\vec{X}]$.
    If $P \in \CorrectPoly$, then $P$ is \kl{represented}
    by a \kl{star-free $\Nat$-polyregular function},
    which is computable given $P$.
\end{lemma}
\begin{proof}
    We prove the result by induction on the number of indeterminates of $P$.
    In the proof, we write $\vec{X}$ for the indeterminates appearing in $P$,
    that is, we assume without loss of generality that all indeterminates are used.

@@

    \textbf{Induction:} Assume that $P$ is not a constant polynomial, and let
    us write $P = P_1 + P_2$ where $P_1$ is the sum of the \kl{maximal
    monomials} of $P$. We compute a bound $K$ such that $Q \defined
    (\Diff{K}{P_1} + \translate{K}(P_2)) \in \Nat[\vec{X}]$ using
    \cref{derivation-stabilises-correct:lem}. In particular, $Q$ is
    \kl{represented} by a \kl{star-free $\Nat$-polyregular function} using
    \cref{n-poly-n-poly:example}, the latter being effectively computable from
    $Q$. Let us now remark that $P_1 \in \Nat[\vec{X}]$, and is therefore
    (effectively) \kl{represented} by a \kl{star-free $\Nat$-polyregular
    function} (using again \cref{n-poly-n-poly:example}). As a consequence,
    $\translate{K}(P) = P_1 + Q$ is (effectively) \kl{represented} by a
    function $f_\Delta$.

    For all partial valuations $\nu \colon \vec{X} \topartial \set{0, \dots,
    K}$ fixing at least one indeterminate, one can use the induction hypothesis
    to compute a \kl{star-free $\Nat$-polyregular function} $f_\nu$ that
    \kl{represents} $\restr{P}{\nu}$. This is possible because we assumed that
    all indeterminates in $\vec{X}$ are used in $P$.

@@

\begin{lemma}
    \label{derivation-translation:lem}
    Let $\vec{X}$ be a tuple of indeterminates,
    and let $P \in \Rel[\vec{X}]$.
    There exists a computable number $K \in \Nat$
    such that the following are equivalent:
    \begin{enumerate}
        \item \label{d-t-correct:item} $P \in \CorrectPoly$,
        \item \label{d-t-transl:item}
            for 
            all partial functions $\nu \colon \vec{X} \topartial \Nat$,
            $\translate{K}(\restr{P}{\nu}) \in \Nat[\vec{X}]$,
        \item \label{d-t-transl-fin:item}
            for all partial functions
            $\nu \colon \vec{X} \topartial \set{0, \dots, K}$,
            $\translate{K}(\restr{P}{\nu}) \in \Nat[\vec{X}]$.
    \end{enumerate}
    In particular, the above properties are decidable.
    \proofref{derivation-translation:lem}
\end{lemma}

@@

\begin{theorem}
    \label{corrected-version:thm}
    Let $\vec{X}$ be a tuple of indeterminates,
    and let $P \in \Rel[\vec{X}]$.
    The following are equivalent:
    \begin{enumerate}
        \item \label{corrected-0:item} $P$ is a \kl{natural binomial polynomial},
        \item \label{corrected-1:item} $P \in \CorrectPoly$,
        \item \label{corrected-2:item} $P$ is \kl{represented} by a \kl{$\Nat$-rational series},
        \item \label{corrected-3:item} $P$ is \kl{represented} by a \kl{$\Nat$-polyregular function},
        \item \label{corrected-4:item} $P$ is \kl{represented} by a \kl{star-free $\Nat$-polyregular function},
    \end{enumerate}
    Furthermore, the properties are decidable, and conversions effective.
\end{theorem}
\begin{proof}
    The implications 
    \cref{corrected-4:item} $\implies$
    \cref{corrected-3:item} $\implies$
    \cref{corrected-2:item} are obvious.
    \cref{lem:correct-to-n-rat} proves
    \cref{corrected-1:item} $\implies$ \cref{corrected-4:item},
    while \cref{n-rat-correct:lem}
    proves 
    \cref{corrected-2:item} $\implies$ \cref{corrected-1:item}.
    Note that the lemmas provide effective conversion procedures,
    and that
    \cref{derivation-translation:lem}
    also provides a decision
    procedure.
\end{proof}

@@

\AP As a consequence, we can also fully characterize polynomials that can be
computed using \kl{$\Rel$-rational series}, as they are precisely those
computable by a difference of two \kl{$\Nat$-rational polynomials}. This drives
us to introduce the class of \intro{integer binomial polynomials}, which are
obtained by $\Rel$-linear combinations of \kl{binomial monomials} of the form
$\binom{X - p}{k}$ for some $k,p \in \Nat$.

\begin{corollary}
    \label{integer-binomial-polynomials:cor}
    Let $P \in \Rat[\vec{X}]$. Then, $P$ is a \kl{$\Rel$-rational polynomial}
    if and only if $P$ is a \kl{integer binomial polynomial}.
\end{corollary}

### 2024-08-14 parts/intro.tex
gigantic rewrite

\AP \kl{Polyregular functions} with a single letter output alphabet can be seen
as having outputs in $\Nat$, and this is why they were introduced respectively
as \kl{$\Nat$-polyregular functions} ($\NPoly$, for \kl{polyregular functions}
with unary output) and \kl{star-free $\Nat$-polyregular functions} ($\NSF$
\kl{for star-free polyregular functions} with unary output)
\cite{DOUE21,DOUE22}. From this point of view, $\NPoly$ is a subclass of a
larger and well-studied class of functions called (non-commutative)
\intro{rational series} \cite{REUT80,BERE88,BERE10}. It has been noticed in
\cite{CDTL23} that \kl{$\Nat$-polyregular functions} correspond to a natural
subclass of \intro{$\Nat$-rational series} ($\intro*\NRat$), another model of
computation that aims at generalizing the notion of regular language to
functions with outputs in a semiring \cite{BERE88,BERE10}. It was frequently
rediscovered in the literature that \kl{$\Nat$-polyregular functions} are a
subclass of \kl{rational series} \cite{SCHU62,KRRC13,CDTL23}.

>>>>

\AP \kl{Polyregular functions} with a single letter output alphabet can be seen
as having outputs in $\Nat$, and this is why they were introduced respectively
as \kl{$\Nat$-polyregular functions} ($\NPoly$, for \kl{polyregular functions}
with unary output) and \kl{star-free $\Nat$-polyregular functions} ($\NSF$
for \kl{star-free polyregular functions} with unary output)
\cite{DOUE21,DOUE22}. From this point of view, $\NPoly$ is a subclass of a
larger and well-studied class of functions called (non-commutative)
\intro{rational series} \cite{REUT80,BERE88,BERE10}. It has been noticed in
\cite{CDTL23} that \kl{$\Nat$-polyregular functions} correspond to a natural
subclass of \intro{$\Nat$-rational series} ($\intro*\NRat$), another model of
computation that aims at generalizing the notion of regular language to
functions with outputs in a semiring \cite{BERE88,BERE10}. It was frequently
rediscovered in the literature that \kl{$\Nat$-polyregular functions} are a
subclass of \kl{rational series} \cite{SCHU62,KRRC13,CDTL23}.
